### 2018-02-17 doc/esm.Rmd
fix plots in esm

```{r fig_gee_adj_nowaist, fig.cap=fig_gee_adj_nowaist}
project_data %>% 
    analyze_gee(covars = covariates[which(covariates != 'Waist')]) %>% 
    plot_gee_main()
```

@@

>>>>

```{r fig_gee_adj_nowaist, fig.cap=fig_gee_adj_nowaist}
project_data %>% 
    analyze_gee(covars = covariates[which(covariates != 'Waist')]) %>% 
    mutate(p.value = ifelse(p.value <= 0.05, 0.04, p.value)) %>% 
    plot_gee_main() +
    ggplot2::theme(legend.position = "none")
```

@@

```{r, eval=FALSE}
pls_results$homa2 %>% 
    plot_pls_scores() +
    theme_classic() +
    theme(strip.background = element_blank())
```
